---
title: "Introduction To Data Mining"
author: "Joshua de la Bruere"
date: "3/30/2020"
output: 
  learnr::tutorial:
    progressive: true
    allow_skip: true
runtime: shiny_prerendered
description: "Welcome to Data Mining With R!"
---

```{r setup, include=FALSE}
library(learnr)
#tutorial_options(exercise.timelimit = 60)
```


## Overview Of the Course
### Topics Covered
This course will cover the following topics:

+ Overview of Data Mining
+ Using visualization for Data Mining
+ Supervised Classification
+ Unsupervised Classification
+ Regression (linear/Logistic)
+ Neural Networks
+ Decision Trees
+ K Nearest neighbors
+ Random Forests
+ Using Tidy Models

### Is this course for you? 

Is this course a good fit for you? Answer these questions to find out. 

```{r course_fit_prereq, echo = FALSE}
question("Are you familiar with the following?", 
         answer("data manipulation in R", correct = T, message = "* Data Manipulation is a required skill"), 
         answer("the Tidyverse", correct = T, message = "* The Tidyverse will be used often in this course"), 
         answer("the concept of Tidy Data", correct = T), 
         type = "multiple", 
         incorrect = "It looks like you're missing a few prerequisits, this course may not be a good fit."
         )

```

```{r course_fit_topics, echo = FALSE}

question("Do you already know how to do the following in R?", 
         answer("creating models in R", message = "This will be covered"), 
         answer("classification, Regression, Neural Nets, and Association Rules" ), 
         answer("None of these", correct = T, message = "Have no fear, these will be covered in this course."),
         type = "multiple",
         incorrect =  "This tutorial will be covering things that you're already familiar with."
         )
```



## Core Ideas in Data Mining

### Variable Types

### Data Gathering

### Data Exploration

### Data Visulization

### Modeling

+ Supervised
+ Unsupervised

### Implementation

### Common Issues




## Data Exploration and Cleaning

### Detecting Outliers

### Dealing With Missing Data

#### Omission

#### Imputation

### Normalization of Data

## Visualization

## Modeling

### Supervised Learning

### Unsupervised Learning

### Over Sampling

### Over Fitting



